%Preamble
%Style section
\documentstyle[graphicx,amscd,amssymb,verbatim,12pt,righttag,color]{amsart}
%documentclass[12pt,psfig,reqno]{amsart}
%\usepackage[usenames]{color} %\color{Red}
\setlength{\textwidth}{15.0cm}
\setlength{\textheight}{22.0cm}
\hoffset=-1cm
\pagestyle {plain}
% \theoremstyle{plain}
%\newtheorem{Thm}{Theorem}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{Def}[theorem]{Definition}
\newtheorem{Prop}[theorem]{Proposition}
\newtheorem{Lem}[theorem]{Lemma}
\newtheorem{Cor}[theorem]{Corollary}
\newtheorem{Rem}[theorem]{Remark}
\newtheorem{Example}[theorem]{Example}
\newtheorem{Coj}[theorem]{Conjecture}
\newtheorem{Main}{Main Theorem}
\renewcommand{\theMain}{}
%Command section
\topmargin=0cm
\errorcontextlines=0
\numberwithin{equation}{section}
\renewcommand{\rm}{\normalshape}
%redefining \rm to mean: change to roman style
\renewcommand{\baselinestretch}{1.1}
%\usepackage{graphicx}
\begin{document}
\begin{center}
{\bf Optional bonus: bonus 15 points for the final exam}
\end{center}
\bigskip
\begin{enumerate}
\item Please complete the following TWO questions by {\bf typing up the solution
and providing us with the figure about the problem.} Handwritten solution will NOT
be graded.
\item For typing up, students are advised to use LaTeX (you can use it at
Overleaf : www.overleaf.com). Students can also use Word File, though it will take
longer time.
\item For Figures, you can use desmos3D, or some other program that you know.
\item Please declare how you work out the problem. e.g. you work in groups with
another students, use Wofram Alpha or even you use ChatGPT or other AI, you have to
declare. Failure of the declaration may result in 0 points.
\item Please submit a PDF file on Canvas by next Friday.
\end{enumerate}
\bigskip
\underline{{\bf Questions.}}
\bigskip
1. Let ${\bf F}(x,y,z) = \sin (x^2) {\bf i}+ xz {\bf j}+ z^2 {\bf k}$.
Evaluate $\int_C {\bf F}\cdot d{\bf r}$ around the curve $C$ of the intersection
of the cylinder $x^2+y^2=4$ with the surface $z = x^2$ in counter-clockwise
direction as viewed from the top on the $z$-axis.
\bigskip
2. Let $E$ be the solid region between the plane $z = 4$ and the paraboloid $z =
x^2+y^2$. Let
$$
{\bf F}(x,y,z) = \left(-\frac13 x^3+e^{z^2}\right){\bf i}+ \left(-\frac13y^3+x\sin
z\right) {\bf j} + 4z{\bf k}.
$$
Let $S$ be the surface that encloses $E$.
Find
$$
\iint\limits_S {\bf F}\cdot d{\bf S}.
$$
\bigskip
\bigskip
\end{document}